(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via D-D Neutron Generator\\ OR \\(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} at 2.76 MeV using a D-D Neutron Generator for Medical Isotope Studies

### 2016-12-23 First_np_Paper/first_np_paper.tex
Updated section 2.1 with first round edits

Neutron activation was carried out via irradiation in the UC Berkeley High-Flux Neutron Generator (HFNG), a D-D neutron generator, seen in \autoref{fig:hfng_a}. This generator extracts deuterium ions from an RF-heated deuterium plasma through using a electric potential-shaping nozzle, forming a flat-profile beam 5 mm in diameter. This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for D-D fusion, producing neutrons with a well-known energy distribution as a function of lab emission angle. Within the center of the target (at 5 mm from the D-D reaction surface), samples may be inserted prior to the HFNG startup, where they are irradiated in a flux of approximately 10$^8$ neutrons/cm$^2$.  A reference model of this target setup may be seen in \autoref{fig:hfng_b}. During irradiation, the machine operates under nominal conditions of a 100-kV deuterium beam extracted at 1-2 mA.

@@

\begin{figure*}
    \centering
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[height=3in]{./figures/Capture.PNG}
        \caption{The UC Berkeley High-Flux Neutron Generator,}
        \label{fig:hfng_a}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
        \includegraphics[height=2in]{./figures/target2.png}
        \caption{Cutaway of the target chamber.}
                \label{fig:hfng_b}
    \end{subfigure}
    \caption{Note: the ion source is approximately 20 cm in diameter, for scale.}
     \label{fig:main_HFNG}
\end{figure*}

>>>>

Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a D-D neutron generator at the University of California Berkeley, seen in  \autoref{fig:hfng_a}. This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam 5 mm in diameter. This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for D-D fusion, producing neutrons with a well-known energy distribution as a function of lab emission angle \cite{Liskien_Paulsen_1973}. Within the center of the target (at 8 mm from the D-D reaction surface), samples may be inserted prior to  HFNG startup. \autoref{fig:hfng_b} displays the target setup. At the time of the presented experiments, the machine operated under nominal conditions of a 100 kV deuterium beam extracted at 1.5 mA, creating a fluence of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$ on the target.

\comment{Karl: Comment or question primarily to Lee: Is it conventional to put photographs of equipment in PRC? I’m not sure it is; yes certainly for NIM, but not sure about PRC.}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[height=3in]{./figures/Capture.PNG}
        \caption{The UC Berkeley High-Flux Neutron Generator,}
        \label{fig:hfng_a}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
        \includegraphics[height=2in]{./figures/target2.png}
        \caption{Cutaway of the target chamber.}
                \label{fig:hfng_b}
    \end{subfigure}
    \caption{Note: the ion source is approximately 20 cm in diameter.}
     \label{fig:main_HFNG}
\end{figure*}
